---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# copulary

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/copulary)](https://CRAN.R-project.org/package=copulary)
<!-- badges: end -->

copulary:

1. make standard copula families available, like the Frank, Gumbel, Gaussian, and empirical copulas -- and even your own copulas, and
2. provides a framework for evaluating copulas.

## Installation

You can install the development version of copulary like so:

``` r
remotes::install_github("probaverse/copulary")
```

## Example

We can make copulas from standard families, such as this Integrated Gamma copula:

```{r example}
library(copulary)
(my_copula <- cop_ig(theta = 3, alpha = 4))
```

We can evaluate different distributional forms, such as the density or cdf:

```{r cars}
# eval_density(my_copula, u = c(0.3, 0.4, 0.6), v = c(0.1, 0.9, 0.4))
# eval_cdf(my_copula, u = c(0.3, 0.4, 0.6), v = c(0.1, 0.9, 0.4))
```

Or, you can enframe the results in a tibble / data frame:

```{r pressure, echo = FALSE}
# enframe_cdf(my_copula, u = c(0.3, 0.4, 0.6), v = c(0.1, 0.9, 0.4))
```
